Experiments with Synthetic Data

### 2022-07-21 dev/notebooks/synthetic.qmd
some more work on streamlining experiments.

```{julia}
using AlgorithmicRecourseDynamics.Experiments
using AlgorithmicRecourseDynamics.Experiments: Experiment
target = 1.0
experiment = Experiment(counterfactual_data, target, models, generators)
```

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 2
n_folds = 5
T = 1000
```

>>>>

```{julia}
# Models:
models = (Bayesian=M_laplace, Plugin=M)
# Generators:
loss = :logitbinarycrossentropy
generators = (
    Greedy=GreedyGenerator(loss=loss), 
    Generic=GenericGenerator(loss=loss),
    REVISE=REVISEGenerator(loss=loss),
    DICE=DiCEGenerator(loss=loss)
)
```

```{julia}
using AlgorithmicRecourseDynamics.Experiments
using AlgorithmicRecourseDynamics.Experiments: Experiment
target = 1.0
experiment = Experiment(counterfactual_data, target, models, generators, 5)
```

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 10
n_folds = 1
T = 1000
```
